### 2014-08-08 paper/paper.tex
Made a few small edits in the paper

There are many established methods of selecting features such as document
frequency, which is simply the number of documents that a word occurs at least
once in. Document frequency has the added benefit of not requiring a class
labels to select features. While document frequency is the only method employed
for this project, many other methods exist, such as Gini Index, Information Gain,
and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
methods rely on the class label in the training set in order to determine how
well the feature discriminates between classes.

@@

Accuracy is used as a secondary performance measure. While more intuitive, it
is not used as a primary evaluation measure due to it's tendency to be biased
by uneven numbers of examples particular labels in the dataset. Accuracy,
henceforth referred to as $Acc$, can be calculate with the following formula:

@@

Where $N$ is equal to the total number of documents in the \textit{test set}.

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal (words with a
document frequency $<$ 1), Or feature normalization. The F-score that is
achieved is \textbf{50.72}.

>>>>

There are many established methods of selecting features such as document
frequency, which is simply the number of documents that a word occurs at least
once in. Document frequency has the added benefit of not requiring a class
labels to select features. While document frequency is the only method employed
for this project, many other methods exist, such as Gini Index, Information
Gain, and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
methods rely on the class label in the \textit{training set} in order to
determine how well the feature discriminates between classes.

@@

Accuracy is used as a secondary performance measure. Accuracy, henceforth
referred to as $Acc$, can be calculate with the following formula:

@@

Where $N$ is equal to the total number of documents in the \textit{test set}.
While more intuitive, it is not used as the primary evaluation measure due to
it's tendency to be biased by uneven numbers of examples of particular labels
in the dataset.

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, rare word removal (words with a
document frequency $<$ 1), Or feature normalization. The F-score that is
achieved is \textbf{50.72}.
